---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# whitetailedSIRS

<!-- badges: start -->
<!-- badges: end -->

The goal of whitetailedSIRS is to provide a simple package to generate epidemic projections in white tailed deer populations using a **S**usceptible-**I**nfected-**R**ecovered-**S**usceptible (SIRS) modeling framework. The outputs of this package are ggplot friendly, and for the most part, we use a list-column workflow when working with multiple simulations. Details on the model can be found in the vignettes.

## Installation

You can install the development version of whitetailedSIRS from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("disease-decision-analysis-and-research/whitetailedSIRS")
```

## Example

This is a basic example to run a simple projection using the base function:


```{r example}
library(whitetailedSIRS)
## basic example code
```


```{r set_parameters}
example_inits <- c(S_wild = 1, 
                   I_wild = 0, 
                   R_wild = 0,
                   S_captive = 1,
                   I_captive = 0,
                   R_captive = 0)

# length of time to run this for  
example_times <-  seq(0, 500, by = 1)

# The parameters we are using in the simulation
example_params <- c(alpha_immunity = 0.03,
                    beta_aero_ww = 0.01,
                    beta_aero_cw = 0.01,
                    beta_aero_cc = 0.02,
                    beta_aero_hw = 0.01,
                    beta_aero_hc = 0.2,
                    beta_dc_ww = 0.01,
                    beta_dc_cw = 0.01,
                    beta_dc_cc = 0.01,
                    phi_cw = 0,
                    phi_wc = 0,
                    gamma_recov = 0.01,
                    I_human = 0.05)

```

```{r run_ode}
library(deSolve)
library(rootSolve)

example_out <- ode(y = example_inits, times = example_times, parms = example_params, func = whitetailedSIRS::simple_sirs)

example_eq <- runsteady(y = example_inits, parms = example_params, func = whitetailedSIRS::simple_sirs)
```

```{r viz_results, message=FALSE}
library(tidyverse)
example_out %>% 
   as_tibble() %>% 
   pivot_longer(-time, names_to = "compartment", values_to = "proportion") %>% 
   separate(compartment, sep = "_", c("sir_type", "pop_type")) %>% 
   mutate(sir_type = factor(sir_type, levels = c("S", "I", "R")),
          pop_type = factor(pop_type, levels = c("wild", "captive"))) %>% 
   ggplot(aes(x = time, y = proportion, color = sir_type, linetype = pop_type)) +
   geom_line() +
   labs(title = "SIR dynamics", y = "Proportion of population", x = "Time in days",
        color = "SIR", linetype = "Population type") +
   theme_bw()

```
```{r warning=FALSE}
example_eq$y %>% 
   as_tibble_row() %>% 
   pivot_longer(cols = everything(), names_to = "compartment", values_to = "proportion") %>% 
   separate(compartment, sep = "_", c("sir_type", "pop_type")) %>% 
   mutate(sir_type = factor(sir_type, levels = c("S", "I", "R")),
          pop_type = factor(pop_type, levels = c("wild", "captive"))) %>% 
   ggplot(aes(x = sir_type, 
              alpha = pop_type,
              y = proportion, fill = sir_type)) +
   geom_col(position = "dodge") +
   labs(title = "Equilibrium proportions", x = "Compartment", alpha = "Population type", fill = "SIR") +
   scale_alpha_discrete(range = c(1, 0.4)) +
   ylim(0, 1) +
   theme_bw()
   
```


