---
title: "example_values"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{example_values}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message=FALSE}
library(whitetailedSIRS)
library(tidyverse)
```


As a first example, we will use the defaults for all the values, and run one projection of the SIRS model. These defaults are produced as random draws from the expert elicitation data.


First, load the data, and generate a random sample for each of the parameters: 

```{r}
set.seed(789)
# load data from package
elicitation_data <- whitetailedSIRS::elicitation_data

# establish number of samples to draw from distributions
nsamples <- 100

# bind samples to the elicitation df
elicitation_data %>% 
   # create a random sample using the parameters depending on the specified distribution
   mutate(my_sample = if_else(family == "log-normal",
                              pmap(list(mu, sd), function(mu, sd) rlnorm(nsamples, mu, sd)),
                              pmap(list(mu, sd), 
                                   function(mu, sd) greybox::rlogitnorm(nsamples, mu, sd)))) -> elicitation_data
   
# for this example, draw just one value for each parameter
elicitation_data %>% 
   transmute(parameter = parameter,
             my_sample = map_dbl(my_sample, 1)) -> elicitation_sample
head(elicitation_sample)

```

From this `elicitation_sample` we can use the values to start setting some of the parameters. We create a simple helper function to extract these values from the data frame. We extract parameters from the expert elicitation to feed into our functions that will later estimate transmission probabilities and contact rates.

```{r}
get_param_val <- function(my_param){
   elicitation_sample %>% 
      filter(parameter == my_param) %>% 
      pull(my_sample)
}
```


```{r}
alpha_immunity <- 1 /get_param_val("Temporary Immunity")

N_w <- rpois(1, 1000)

C_nu <- get_param_val("Viral Load") * 10^5.6

t_contact_deer_deer <- get_param_val("Deer Proximity Duration (minutes)") / 60
t_contact_deer_human_rural <- get_param_val("Deer-Human Proximity Duration, Rural (minutes)") / 60
t_contact_deer_human_suburb <- get_param_val("Deer-Human Proximity Duration, Suburban (minutes)") / 60
t_contact_deer_human_capt <- get_param_val("Deer-Human Proximity Duration, Captive (minutes)") / 60

r_deer <- get_param_val("Dose-Response")
```

```{r}
c_ww <- calc_contact_rate()
c_cc <- get_param_val("Deer-Deer Proximity Rate, Captive (per day)")
c_cw <- 0.00072 / get_param_val("Direct Contact Probability")
c_hw_rural <- get_param_val("Deer-Human Proximity Rate, Rural (per 120 days)") / 120
c_hw_suburban <- get_param_val("Deer-Human Proximity Rate, Suburban (per 120 days)") / 120
c_hc <- get_param_val("Deer-Human Proximity Rate, Captive (per 120 days)") /120
```


```{r}
nu_aero_deer_deer <- calc_nu_aero(C_nu = C_nu, t_contact = t_contact_deer_deer, r = r_deer)
nu_aero_deer_human_rural <- calc_nu_aero(C_nu = C_nu, t_contact = t_contact_deer_human_rural, r = r_deer)
nu_aero_deer_human_capt <- calc_nu_aero(C_nu = C_nu, t_contact = t_contact_deer_human_capt, r = r_deer)

nu_dc_deer_deer <- calc_nu_dc(C_nu = C_nu)

sigma_dc <- get_param_val("Direct Contact Probability")

```

```{r}
beta_aero_ww <- c_ww * nu_aero_deer_deer
beta_aero_cw <- c_cw * nu_aero_deer_deer
beta_aero_cc <- c_cc * nu_aero_deer_deer
beta_aero_hw <- c_hw_rural * nu_aero_deer_human_rural
beta_aero_hc <- c_hc * nu_aero_deer_human_capt


beta_dc_ww <- c_ww * sigma_dc * nu_dc_deer_deer
beta_dc_cw <- c_cw * sigma_dc * nu_dc_deer_deer
beta_dc_cc <- c_cc * sigma_dc * nu_dc_deer_deer
```


```{r}
example_inits <- c(S_wild = 1, 
                   I_wild = 0, 
                   R_wild = 0,
                   S_captive = 1,
                   I_captive = 0,
                   R_captive = 0)

# length of time to run this for  
example_times <-  seq(0, 120, by = 1)

# The parameters we are using in the simulation
example_params <- c(alpha_immunity = alpha_immunity,
                    beta_aero_ww = beta_aero_ww,
                    beta_aero_cw = beta_aero_cw,
                    beta_aero_cc = beta_aero_cc,
                    beta_aero_hw = beta_aero_hw,
                    beta_aero_hc = beta_aero_hc,
                    beta_dc_ww = beta_dc_ww,
                    beta_dc_cw = beta_dc_cw,
                    beta_dc_cc = beta_dc_cc,
                    phi_cw = 0,
                    phi_wc = 0,
                    gamma_recov = 1/6,
                    I_human = 0.05)

```

```{r run_ode}
library(deSolve)
library(rootSolve)

example_out <- ode(y = example_inits, times = example_times, parms = example_params, func = whitetailedSIRS::simple_sirs)

example_eq <- runsteady(y = example_inits, parms = example_params, func = whitetailedSIRS::simple_sirs)
```

```{r viz_results}

example_out %>% 
   as_tibble() %>% 
   pivot_longer(-time, names_to = "compartment", values_to = "proportion") %>% 
   separate(compartment, sep = "_", c("sir_type", "pop_type")) %>% 
   mutate(sir_type = factor(sir_type, levels = c("S", "I", "R")),
          pop_type = factor(pop_type, levels = c("wild", "captive"))) %>% 
   ggplot(aes(x = time, y = proportion, color = sir_type, linetype = pop_type)) +
   geom_line() +
   labs(title = "SIR dynamics", y = "Proportion of population", x = "Time in days",
        color = "SIR", linetype = "Population type") +
   theme_bw()

```

```{r warning=FALSE}
example_eq$y %>% 
   as_tibble_row() %>% 
   pivot_longer(cols = everything(), names_to = "compartment", values_to = "proportion") %>% 
   separate(compartment, sep = "_", c("sir_type", "pop_type")) %>% 
   mutate(sir_type = factor(sir_type, levels = c("S", "I", "R")),
          pop_type = factor(pop_type, levels = c("wild", "captive"))) %>% 
   ggplot(aes(x = sir_type, 
              alpha = pop_type,
              y = proportion, fill = sir_type)) +
   geom_col(position = "dodge") +
   labs(title = "Equilibrium proportions", x = "Compartment", alpha = "Population type", fill = "SIR") +
   scale_alpha_discrete(range = c(1, 0.4)) +
   ylim(0, 1) +
   theme_bw()
   
```


Do worflow for 100 sampled parameters:

