---
title: "Evaluation of management alternatives across systems"
subtitle: "Analysis referenced in Cook et al. In Prep"
authors: "Elias Rosenblatt"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Evaluation of management alternatives across systems}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include = FALSE}
library(whitetailedSIRS)
library(tidyverse)
library(deSolve)
library(rootSolve)
library(binom)
library(kableExtra)
```

##Introduction: 
Here, we run outbreak simulations to estimate the effects of various management alternatives on the dynamics of a SARS-CoV-2 outbreak in wild and captive white-tailed deer. We considered captive:wild systems that are separated by a fence. These management alternatives may be implemented in both wild and captive populations, or in one scenario. 

We focus on 11 alternatives, ranging across agriculture, public health, and wildlife sectors. These alternatives are detailed in Cook et al. In Prep., and include:

```{r}
ActionTable <- data.frame(Alternative = c("Reduce wild density by 10%", "Reduce wild density by 25%", "Eliminate baiting", "Pause Research", "Restrict human interactions with deer","PPE, Wild" , "PPE, Captive", "PPE, Both", "Vaccinate captive deer", "Vaccinate and boost captive deer", "Double-fence captive facilities", "Increase air exchange rate in intensive facilities"), Sector = c("Wildlife", "Wildlife", "Wildlife", "Wildlife", "Public Health","Public Health","Public Health","Public Health", "Agriculture", "Agriculture","Agriculture", "Agriculture"), Ranch_Rural_System = c(TRUE,TRUE,TRUE,TRUE,TRUE,TRUE,TRUE,TRUE,TRUE,TRUE,TRUE,FALSE), Ranch_Suburban_System = c(TRUE,TRUE,TRUE,TRUE,TRUE,TRUE,TRUE,TRUE,TRUE,TRUE,TRUE,FALSE), Intensive_Facility_Rural_System = c(TRUE,TRUE,TRUE,TRUE,TRUE,TRUE,TRUE,TRUE,TRUE,TRUE,TRUE,TRUE), Intensive_Facility_Suburban_System = c(TRUE,TRUE,TRUE,TRUE,TRUE,TRUE,TRUE,TRUE,TRUE,TRUE,TRUE,TRUE))

ActionTable %>%
  kbl() %>%
  kable_paper("hover", full_width = F)

```
##Common Parameters
First, we set basic simulation parameters across all simulations.
```{r base_simulations, include = FALSE}
set.seed(23)
nsamples <- 200
I_human_null <- 0.05
times <- seq(0, 120, by = 1)
```
We bring in elicitation data for various parameters included in these simulations.
```{r, include = FALSE}
elicitation_data <- draw_elicitation_samples(nsamples = nsamples)
```

We can then define a number of parameters that will be used in every system in which we want to test alternatives.
```{r shared parameters, include = FALSE}
nWild <- rpois(nsamples,1000) #Abundance
A_w <- 100 #Area
habitat <- "med" #Habitat classification

epsilon_dc <- get_EE_param_vals(data = elicitation_data, my_param = "Direct Contact Probability") #Probability of direct contact between deer, given proximity.

C_nu_human <- rnorm(n = nsamples, mean = 10^5.6, sd = 10^1.2)#viral load in humans (genomic copies per ml)
C_nu_deer <- 10^5.6 * get_EE_param_vals(data = elicitation_data, my_param = "Viral Load") #viral load in deer saliva, relative to humans (genomic copies per ml)

r_deer <- get_EE_param_vals(data = elicitation_data, my_param = "Dose-Response")# Dose response coefficient for deer and SARS-CoV-2

t_contact_deer_deer_null <- get_EE_param_vals(data = elicitation_data, my_param = "Deer Proximity Duration (minutes)") #Estimate duration of proximity event...

gamma_recov <- rep(1/6, nsamples) #Recovery rate from infection (6 days)
alpha_immunity_null <- 1 / get_EE_param_vals(data = elicitation_data, my_param = 'Temporary Immunity') #Rate of temporary immunity loss

#shared derived parameter
sigma_dc_deer_deer_null <- calc_sigma_dc(C_nu = C_nu_deer, nsamples = nsamples) #Infection probability for fluid transmission
```

##Scenario parameters
Here, we define parameter values used for the baseline projection for each system.

###Outdoor ranch facilities

```{r}
#Ranch Parameters
omega_cc_ranch <- calc_contact_rate(nsamples = nsamples, type_contact = habitat, N_w = nWild)*(get_EE_param_vals(data = elicitation_data, my_param = "Proximity rate with baiting (17 events without baiting)")/17) #Deer-to-deer proximity rate in ranch context, mimicing wild proximity rates with the influence of baiting (events per day).
omega_hc_ranch <- get_EE_param_vals(data = elicitation_data, my_param = "Deer-Human Proximity Rate, Suburban (per 120 days)") /120 #Human-to-deer proximity rate in ranch context, mimicing suburban proximitty rates (events per day).
#Infection probability calculation of aerosol transmission from humans-to-deer
t_contact_deer_human_ranch <- get_EE_param_vals(data = elicitation_data, my_param = "Deer-Human Proximity Duration, Captive (minutes)") #Estimate duration 
#derived ranch parameters
sigma_aero_deer_deer_ranch <- calc_sigma_aero(C_nu = C_nu_deer,
                                        t_contact = t_contact_deer_deer_null / 60,
                                        r = r_deer, nsamples = nsamples) #...and estimate probability of infection given that duration of proximity event.

sigma_aero_deer_human_ranch <- calc_sigma_aero(ER = 0.53, C_nu = C_nu_human, 
                                        t_contact = t_contact_deer_human_ranch / 60,
                                        r = r_deer, nsamples = nsamples)#... and calculate infection probability given the duration of a human-deer proximity event.
```

###Intensive facilities
```{r}
#Intensive facility parameters
omega_cc_intensive <- get_EE_param_vals(data = elicitation_data, my_param = "Deer-Deer Proximity Rate, Captive (per day)") #Deer-to-deer proximity rate in intensive context, mimicing wild proximity rates with the influence of baiting (events per day).
omega_hc_intensive <- get_EE_param_vals(data = elicitation_data, my_param = "Deer-Human Proximity Rate, Captive (per 120 days)") /120 #Human-to-deer proximity rate in intensive context, mimicing suburban proximitty rates (events per day).
#Infection probability calculation of aerosol transmission from humans-to-deer
t_contact_deer_human_intensive <- get_EE_param_vals(data = elicitation_data, my_param = "Deer-Human Proximity Duration, Captive (minutes)") #Estimate duration 
#derived intensive parameters
sigma_aero_deer_deer_intensive <- calc_sigma_aero(C_nu = C_nu_deer,
                                        t_contact = t_contact_deer_deer_null / 60,
                                        r = r_deer, nsamples = nsamples, AER = rep(1, nsamples)) #...and estimate probability of infection given that duration of proximity event.

sigma_aero_deer_human_intensive <- calc_sigma_aero(ER = 0.53, C_nu = C_nu_human, 
                                        t_contact = t_contact_deer_human_intensive / 60,
                                        r = r_deer, nsamples = nsamples, AER = rep(1, nsamples))#... and calculate infection probability given the duration of a human-deer proximity event.
```

###Fenceline proximity rate
Captive and wild deer are separated by a single fence that allows proximity and direct contact through the fenceline.
```{r}
#Fenceline
omega_cw <- 0.00072 / get_EE_param_vals(data = elicitation_data, my_param = "Direct Contact Probability") #Deer-to-deer proximity rate along fenceline (events per day).
```

###Suburban
```{r}
#Wild, suburban parameters
omega_ww_suburban <- calc_contact_rate(nsamples = nsamples, type_contact = habitat, N_w = nWild)*(get_EE_param_vals(data = elicitation_data, my_param = "Proximity rate with baiting (17 events without baiting)")/17)
omega_hw_suburban <- get_EE_param_vals(data = elicitation_data, my_param = "Deer-Human Proximity Rate, Suburban (per 120 days)") /120

t_contact_deer_human_suburban <- get_EE_param_vals(data = elicitation_data, my_param = "Deer-Human Proximity Duration, Suburban (minutes)")

#derived wild parameters
sigma_aero_deer_deer_suburban <- calc_sigma_aero(C_nu = C_nu_deer,
                                        t_contact = t_contact_deer_deer_null / 60,
                                        r = r_deer, nsamples = nsamples, AER = rep(4, nsamples))

sigma_aero_deer_human_suburban <- calc_sigma_aero(ER = 0.53, C_nu = C_nu_human, 
                                        t_contact = t_contact_deer_human_suburban / 60,
                                        r = r_deer, nsamples = nsamples, AER = rep(4, nsamples))
```

###Rural
```{r}
#Wild, rural parameters
omega_ww_rural <- calc_contact_rate(nsamples = nsamples, type_contact = habitat, N_w = nWild)*(get_EE_param_vals(data = elicitation_data, my_param = "Proximity rate with baiting (17 events without baiting)")/17)
omega_hw_rural <- get_EE_param_vals(data = elicitation_data, my_param = "Deer-Human Proximity Rate, Rural (per 120 days)") /120

t_contact_deer_human_rural <- get_EE_param_vals(data = elicitation_data, my_param = "Deer-Human Proximity Duration, Rural (minutes)")

#derived wild parameters
sigma_aero_deer_deer_rural <- calc_sigma_aero(C_nu = C_nu_deer,
                                        t_contact = t_contact_deer_deer_null / 60,
                                        r = r_deer, nsamples = nsamples, AER = rep(4, nsamples))

sigma_aero_deer_human_rural <- calc_sigma_aero(ER = 0.53, C_nu = C_nu_human, 
                                        t_contact = t_contact_deer_human_rural / 60,
                                        r = r_deer, nsamples = nsamples, AER = rep(4, nsamples))
```

## Establish Systems and Test Alternatives
Below we define a captive-wild system, simulate SARS-CoV-2 outbreaks with no interventions, and then apply the 12 candidate interventions by altering a relevant parameter. All 13 simulations (1 no action + 12 interventions) are combined into one data frame at the end of each code chunk.

### Combined system of outdoor ranch facilities and wild deer in a suburban setting
```{r}
ranch_suburban.inits.fall <- initial_compartments(draws = nsamples)
ranch_suburban.inits.steady <- initial_compartments(draws = nsamples, steady = TRUE)


ranch_suburban.params <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_suburban, omega_cw = omega_cw, omega_cc = omega_cc_ranch,
                            omega_hw = omega_hw_suburban, omega_hc = omega_hc_ranch,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_suburban, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_ranch, sigma_aero_deer_human_wild = sigma_aero_deer_human_suburban, sigma_aero_deer_human_capt = sigma_aero_deer_human_ranch, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_ranch_suburban_null <- run(iter = nsamples, initial_compartments = ranch_suburban.inits.fall, initial_compartments_steady = ranch_suburban.inits.steady, params = ranch_suburban.params, times = times, name = "Baseline")

#Alternatives
#1. 10% density reduction
omega_ww_alt1_density.red.10 <- whitetailedSIRS::calc_contact_rate(nsamples = nsamples, type_contact = habitat, N_w = nWild*0.9)*(get_EE_param_vals(data = elicitation_data, my_param = "Proximity rate with baiting (17 events without baiting)")/17) 

ranch_suburban.params_alt1 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_alt1_density.red.10, omega_cw = omega_cw, omega_cc = omega_cc_ranch,
                            omega_hw = omega_hw_suburban, omega_hc = omega_hc_ranch,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_suburban, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_ranch, sigma_aero_deer_human_wild = sigma_aero_deer_human_suburban, sigma_aero_deer_human_capt = sigma_aero_deer_human_ranch, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_ranch_suburban_alt1 <- run(iter = nsamples, initial_compartments = ranch_suburban.inits.fall, initial_compartments_steady = ranch_suburban.inits.steady, params = ranch_suburban.params_alt1, times = times, name = "Reduce wild density by 10%")

#2. 25% density reduction
omega_ww_alt2_density.red.25 <- whitetailedSIRS::calc_contact_rate(nsamples = nsamples, type_contact = habitat, N_w = nWild*0.75)*(get_EE_param_vals(data = elicitation_data, my_param = "Proximity rate with baiting (17 events without baiting)")/17)

ranch_suburban.params_alt2 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_alt2_density.red.25, omega_cw = omega_cw, omega_cc = omega_cc_ranch,
                            omega_hw = omega_hw_suburban, omega_hc = omega_hc_ranch,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_suburban, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_ranch, sigma_aero_deer_human_wild = sigma_aero_deer_human_suburban, sigma_aero_deer_human_capt = sigma_aero_deer_human_ranch, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_ranch_suburban_alt2 <- run(iter = nsamples, initial_compartments = ranch_suburban.inits.fall, initial_compartments_steady = ranch_suburban.inits.steady, params = ranch_suburban.params_alt2, times = times, name = "Reduce wild density by 25%")

#3. Eliminate baiting
omega_ww_alt3_no.baiting <- whitetailedSIRS::calc_contact_rate(nsamples = nsamples, type_contact = habitat, N_w = nWild*0.75)

ranch_suburban.params_alt3 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_alt3_no.baiting, omega_cw = omega_cw, omega_cc = omega_cc_ranch,
                            omega_hw = omega_hw_suburban, omega_hc = omega_hc_ranch,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_suburban, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_ranch, sigma_aero_deer_human_wild = sigma_aero_deer_human_suburban, sigma_aero_deer_human_capt = sigma_aero_deer_human_ranch, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_ranch_suburban_alt3 <- run(iter = nsamples, initial_compartments = ranch_suburban.inits.fall, initial_compartments_steady = ranch_suburban.inits.steady, params = ranch_suburban.params_alt3, times = times, name = "Eliminate baiting")

#4. Pause research (assuming random 1-50% of human-wild deer interaction)
omega_hw_alt4_pause.research <- omega_hw_suburban*runif(nsamples, min = 0.5, max = 0.99) #reduce human deer proximity rate in the wild up to 50%

ranch_suburban.params_alt4 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_suburban, omega_cw = omega_cw, omega_cc = omega_cc_ranch,
                            omega_hw = omega_hw_alt4_pause.research, omega_hc = omega_hc_ranch,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_suburban, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_ranch, sigma_aero_deer_human_wild = sigma_aero_deer_human_suburban, sigma_aero_deer_human_capt = sigma_aero_deer_human_ranch, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_ranch_suburban_alt4 <- run(iter = nsamples, initial_compartments = ranch_suburban.inits.fall, initial_compartments_steady = ranch_suburban.inits.steady, params = ranch_suburban.params_alt4, times = times, name = "Pause Research")

#5. Require PPE for humans in wild settings
sigma_aero_deer_human_wild_alt5_PPE <- calc_sigma_aero(ER = 0.53, C_nu = C_nu_human, t_contact = t_contact_deer_human_suburban/60, r = r_deer, V_d = 0.009*runif(nsamples, min = (1-0.994), max = (1-0.509)), nsamples = nsamples)

ranch_suburban.params_alt5 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_suburban, omega_cw = omega_cw, omega_cc = omega_cc_ranch,
                            omega_hw = omega_hw_suburban, omega_hc = omega_hc_ranch,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_suburban, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_ranch, sigma_aero_deer_human_wild = sigma_aero_deer_human_wild_alt5_PPE, sigma_aero_deer_human_capt = sigma_aero_deer_human_ranch, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_ranch_suburban_alt5 <- run(iter = nsamples, initial_compartments = ranch_suburban.inits.fall, initial_compartments_steady = ranch_suburban.inits.steady, params = ranch_suburban.params_alt5, times = times, name = "PPE, Wild")

#6. Require PPE for humans in captive settings
sigma_aero_deer_human_capt_alt6_PPE <- calc_sigma_aero(ER = 0.53, C_nu = C_nu_human, t_contact = t_contact_deer_human_ranch/60, r = r_deer, V_d = 0.009*runif(nsamples, min = (1-0.994), max = (1-0.509)), nsamples = nsamples)

ranch_suburban.params_alt6 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_suburban, omega_cw = omega_cw, omega_cc = omega_cc_ranch,
                            omega_hw = omega_hw_suburban, omega_hc = omega_hc_ranch,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_suburban, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_ranch, sigma_aero_deer_human_wild = sigma_aero_deer_human_suburban, sigma_aero_deer_human_capt = sigma_aero_deer_human_capt_alt6_PPE, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_ranch_suburban_alt6 <- run(iter = nsamples, initial_compartments = ranch_suburban.inits.fall, initial_compartments_steady = ranch_suburban.inits.steady, params = ranch_suburban.params_alt6, times = times, name = "PPE, Captive")

#7. Require PPE for humans in wild and captive settings (use derived parameters from 5 and 6)

ranch_suburban.params_alt7 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_suburban, omega_cw = omega_cw, omega_cc = omega_cc_ranch,
                            omega_hw = omega_hw_suburban, omega_hc = omega_hc_ranch,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_suburban, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_ranch, sigma_aero_deer_human_wild = sigma_aero_deer_human_wild_alt5_PPE, sigma_aero_deer_human_capt = sigma_aero_deer_human_capt_alt6_PPE, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_ranch_suburban_alt7 <- run(iter = nsamples, initial_compartments = ranch_suburban.inits.fall, initial_compartments_steady = ranch_suburban.inits.steady, params = ranch_suburban.params_alt7, times = times, name = "PPE, Both")

#8. Vaccinate captive deer (start with r_captive = 1)
ranch_suburban.inits_alt8 <- initial_compartments(draws = nsamples, S_captive_prop = 0, R_captive_prop = 1)
ranch_suburban.inits_alt8.steady <- initial_compartments(draws = nsamples, S_captive_prop = 0, R_captive_prop = 1, steady = TRUE)

proj_ranch_suburban_alt8 <- run(iter = nsamples, initial_compartments = ranch_suburban.inits_alt8, initial_compartments_steady = ranch_suburban.inits_alt8.steady,params = ranch_suburban.params, times = times, name = "Vaccinate captive deer")

#9. Vaccinate and boost captive deer (start with r_captive = 1)
ranch_suburban.inits_alt9 <- initial_compartments(draws = nsamples, S_captive_prop = 0, R_captive_prop = 1)
ranch_suburban.inits_alt9.steady <- initial_compartments(draws = nsamples, S_captive_prop = 0, R_captive_prop = 1, steady = TRUE)

boost_alt9 <- rep(0.9,nsamples)

ranch_suburban.params_alt9 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_suburban, omega_cw = omega_cw, omega_cc = omega_cc_ranch,
                            omega_hw = omega_hw_suburban, omega_hc = omega_hc_ranch,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_suburban, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_ranch, sigma_aero_deer_human_wild = sigma_aero_deer_human_suburban, sigma_aero_deer_human_capt = sigma_aero_deer_human_ranch, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = boost_alt9)


proj_ranch_suburban_alt9 <- run(iter = nsamples, initial_compartments = ranch_suburban.inits_alt9, initial_compartments_steady = ranch_suburban.inits_alt9.steady, params = ranch_suburban.params_alt9, times = times, name = "Vaccinate and boost captive deer")

#10. Double fence captive facilities
omega_cw_alt10 <- rep(0, nsamples)

ranch_suburban.params_alt10 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_suburban, omega_cw = omega_cw_alt10, omega_cc = omega_cc_ranch,
                            omega_hw = omega_hw_suburban, omega_hc = omega_hc_ranch,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_suburban, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_ranch, sigma_aero_deer_human_wild = sigma_aero_deer_human_suburban, sigma_aero_deer_human_capt = sigma_aero_deer_human_ranch, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0,nsamples))


proj_ranch_suburban_alt10 <- run(iter = nsamples, initial_compartments = ranch_suburban.inits.fall, initial_compartments_steady = ranch_suburban.inits.steady, params = ranch_suburban.params_alt10, times = times, name = "Double-fence captive facilities")

#11. Restrict human interaction (using proportional reduction from suburban to rural)
human_restrictions <- (get_EE_param_vals(data = elicitation_data, my_param = "Deer-Human Proximity Rate, Rural (per 120 days)") / 120)/(get_EE_param_vals(data = elicitation_data, my_param = "Deer-Human Proximity Rate, Suburban (per 120 days)") / 120)

ranch_suburban.params_alt11 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_suburban, omega_cw = omega_cw, omega_cc = omega_cc_ranch,
                            omega_hw = omega_hw_suburban*human_restrictions, omega_hc = omega_hc_ranch,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_suburban, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_ranch, sigma_aero_deer_human_wild = sigma_aero_deer_human_suburban, sigma_aero_deer_human_capt = sigma_aero_deer_human_ranch, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0,nsamples))


proj_ranch_suburban_alt11 <- run(iter = nsamples, initial_compartments = ranch_suburban.inits.fall, initial_compartments_steady = ranch_suburban.inits.steady, params = ranch_suburban.params_alt11, times = times, name = "Restrict human interactions")

#12. Improve indoor facility air exchange (does not apply to outdoor ranch facilities)

proj_ranch_suburban <- rbind(proj_ranch_suburban_null, proj_ranch_suburban_alt1, proj_ranch_suburban_alt2, proj_ranch_suburban_alt3, proj_ranch_suburban_alt4, proj_ranch_suburban_alt5, proj_ranch_suburban_alt6, proj_ranch_suburban_alt7, proj_ranch_suburban_alt8, proj_ranch_suburban_alt9, proj_ranch_suburban_alt10, proj_ranch_suburban_alt11)
```

####Calcualte prevalence, cumulative infections, and persistence for interventions in the outdoor ranch : wild, suburban system
```{r, message=FALSE, warning=FALSE}
persist.threshold <- 0.001

proj_ranch_suburban %>%
  mutate(steady_sir = map(steady_state, "y"),
         steady_sir = map(steady_sir, as_tibble_row)) %>%
  pull(steady_sir) %>%
  list_rbind(names_to = "run_id") %>%
  mutate(., persistWild = I_wild > persist.threshold, persistCaptive = I_captive > persist.threshold) %>%
  select(., run_id, persistWild, persistCaptive) %>%
  arrange(., run_id) -> Persist_ranch_suburban_df

proj_ranch_suburban %>%
  mutate(ode_df = map(ode_proj, as.data.frame)) %>%
  pull(ode_df) %>%
  list_rbind(names_to = "run_id") %>% 
  mutate(., Complex = rep("Outdoor ranch and suburban deer",nrow(.)), Alternative = c(rep(unique(proj_ranch_suburban$Context)[1],length(times)*nsamples),rep(unique(proj_ranch_suburban$Context)[2],length(times)*nsamples), rep(unique(proj_ranch_suburban$Context)[3],length(times)*nsamples),rep(unique(proj_ranch_suburban$Context)[4],length(times)*nsamples), rep(unique(proj_ranch_suburban$Context)[5],length(times)*nsamples), rep(unique(proj_ranch_suburban$Context)[6],length(times)*nsamples), rep(unique(proj_ranch_suburban$Context)[7],length(times)*nsamples),rep(unique(proj_ranch_suburban$Context)[8],length(times)*nsamples),rep(unique(proj_ranch_suburban$Context)[9],length(times)*nsamples),rep(unique(proj_ranch_suburban$Context)[10],length(times)*nsamples),rep(unique(proj_ranch_suburban$Context)[11],length(times)*nsamples),rep(unique(proj_ranch_suburban$Context)[12],length(times)*nsamples))) %>% 
  group_by(Complex,Alternative, run_id) %>% 
  summarize(meanWild = mean(I_wild), meanCaptive = mean(I_captive), 
            cumulativeWild = last(I_wild_cumulative), cumulativeCaptive = last(I_captive_cumulative)) %>% 
   merge(.,Persist_ranch_suburban_df, by = "run_id")-> alternatives_for_ranch_suburban_complex
```

### Combined system of outdoor ranch facilities and wild deer in a rural setting

```{r}
ranch_rural.inits.fall <- initial_compartments(draws = nsamples)
ranch_rural.inits.steady <- initial_compartments(draws = nsamples, steady = TRUE)

ranch_rural.params <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_rural, omega_cw = omega_cw, omega_cc = omega_cc_ranch,
                            omega_hw = omega_hw_rural, omega_hc = omega_hc_ranch,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_rural, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_ranch, sigma_aero_deer_human_wild = sigma_aero_deer_human_rural, sigma_aero_deer_human_capt = sigma_aero_deer_human_ranch, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_ranch_rural_null <- run(iter = nsamples, initial_compartments = ranch_rural.inits.fall, initial_compartments_steady = ranch_rural.inits.steady, params = ranch_rural.params, times = times, name = "Baseline")

#Alternatives
#1. 10% density reduction
omega_ww_alt1_density.red.10 <- whitetailedSIRS::calc_contact_rate(nsamples = nsamples, type_contact = habitat, N_w = nWild*0.9)*(get_EE_param_vals(data = elicitation_data, my_param = "Proximity rate with baiting (17 events without baiting)")/17) 

ranch_rural.params_alt1 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_alt1_density.red.10, omega_cw = omega_cw, omega_cc = omega_cc_ranch,
                            omega_hw = omega_hw_rural, omega_hc = omega_hc_ranch,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_rural, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_ranch, sigma_aero_deer_human_wild = sigma_aero_deer_human_rural, sigma_aero_deer_human_capt = sigma_aero_deer_human_ranch, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_ranch_rural_alt1 <- run(iter = nsamples, initial_compartments = ranch_rural.inits.fall, initial_compartments_steady = ranch_rural.inits.steady, params = ranch_rural.params_alt1, times = times, name = "Reduce wild density by 10%")

#2. 25% density reduction
omega_ww_alt2_density.red.25 <- whitetailedSIRS::calc_contact_rate(nsamples = nsamples, type_contact = habitat, N_w = nWild*0.75)*(get_EE_param_vals(data = elicitation_data, my_param = "Proximity rate with baiting (17 events without baiting)")/17)

ranch_rural.params_alt2 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_alt2_density.red.25, omega_cw = omega_cw, omega_cc = omega_cc_ranch,
                            omega_hw = omega_hw_rural, omega_hc = omega_hc_ranch,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_rural, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_ranch, sigma_aero_deer_human_wild = sigma_aero_deer_human_rural, sigma_aero_deer_human_capt = sigma_aero_deer_human_ranch, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_ranch_rural_alt2 <- run(iter = nsamples, initial_compartments = ranch_rural.inits.fall, initial_compartments_steady = ranch_rural.inits.steady, params = ranch_rural.params_alt2, times = times, name = "Reduce wild density by 25%")

#3. Eliminate baiting
omega_ww_alt3_no.baiting <- whitetailedSIRS::calc_contact_rate(nsamples = nsamples, type_contact = habitat, N_w = nWild*0.75)

ranch_rural.params_alt3 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_alt3_no.baiting, omega_cw = omega_cw, omega_cc = omega_cc_ranch,
                            omega_hw = omega_hw_rural, omega_hc = omega_hc_ranch,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_rural, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_ranch, sigma_aero_deer_human_wild = sigma_aero_deer_human_rural, sigma_aero_deer_human_capt = sigma_aero_deer_human_ranch, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_ranch_rural_alt3 <- run(iter = nsamples, initial_compartments = ranch_rural.inits.fall, initial_compartments_steady = ranch_rural.inits.steady, params = ranch_rural.params_alt3, times = times, name = "Eliminate baiting")

#4. Pause research (assuming random 1-50% of human-wild deer interaction)
omega_hw_alt4_pause.research <- omega_hw_rural*runif(nsamples, min = 0.5, max = 0.99) #reduce human deer proximity rate in the wild up to 50%

ranch_rural.params_alt4 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_rural, omega_cw = omega_cw, omega_cc = omega_cc_ranch,
                            omega_hw = omega_hw_alt4_pause.research, omega_hc = omega_hc_ranch,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_rural, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_ranch, sigma_aero_deer_human_wild = sigma_aero_deer_human_rural, sigma_aero_deer_human_capt = sigma_aero_deer_human_ranch, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_ranch_rural_alt4 <- run(iter = nsamples, initial_compartments = ranch_rural.inits.fall, initial_compartments_steady = ranch_rural.inits.steady, params = ranch_rural.params_alt4, times = times, name = "Pause Research")

#5. Require PPE for humans in wild settings
sigma_aero_deer_human_wild_alt5_PPE <- calc_sigma_aero(ER = 0.53, C_nu = C_nu_human, t_contact = t_contact_deer_human_rural/60, r = r_deer, V_d = 0.009*runif(nsamples, min = (1-0.994), max = (1-0.509)), nsamples = nsamples)

ranch_rural.params_alt5 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_rural, omega_cw = omega_cw, omega_cc = omega_cc_ranch,
                            omega_hw = omega_hw_rural, omega_hc = omega_hc_ranch,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_rural, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_ranch, sigma_aero_deer_human_wild = sigma_aero_deer_human_wild_alt5_PPE, sigma_aero_deer_human_capt = sigma_aero_deer_human_ranch, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_ranch_rural_alt5 <- run(iter = nsamples, initial_compartments = ranch_rural.inits.fall, initial_compartments_steady = ranch_rural.inits.steady, params = ranch_rural.params_alt5, times = times, name = "PPE, Wild")

#6. Require PPE for humans in captive settings
sigma_aero_deer_human_capt_alt6_PPE <- calc_sigma_aero(ER = 0.53, C_nu = C_nu_human, t_contact = t_contact_deer_human_ranch/60, r = r_deer, V_d = 0.009*runif(nsamples, min = (1-0.994), max = (1-0.509)), nsamples = nsamples)

ranch_rural.params_alt6 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_rural, omega_cw = omega_cw, omega_cc = omega_cc_ranch,
                            omega_hw = omega_hw_rural, omega_hc = omega_hc_ranch,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_rural, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_ranch, sigma_aero_deer_human_wild = sigma_aero_deer_human_rural, sigma_aero_deer_human_capt = sigma_aero_deer_human_capt_alt6_PPE, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_ranch_rural_alt6 <- run(iter = nsamples, initial_compartments = ranch_rural.inits.fall, initial_compartments_steady = ranch_rural.inits.steady, params = ranch_rural.params_alt6, times = times, name = "PPE, Captive")

#7. Require PPE for humans in wild and captive settings (use derived parameters from 5 and 6)

ranch_rural.params_alt7 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_rural, omega_cw = omega_cw, omega_cc = omega_cc_ranch,
                            omega_hw = omega_hw_rural, omega_hc = omega_hc_ranch,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_rural, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_ranch, sigma_aero_deer_human_wild = sigma_aero_deer_human_wild_alt5_PPE, sigma_aero_deer_human_capt = sigma_aero_deer_human_capt_alt6_PPE, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_ranch_rural_alt7 <- run(iter = nsamples, initial_compartments = ranch_rural.inits.fall, initial_compartments_steady = ranch_rural.inits.steady, params = ranch_rural.params_alt7, times = times, name = "PPE, Both")

#8. Vaccinate captive deer (start with r_captive = 1)
ranch_rural.inits_alt8 <- initial_compartments(draws = nsamples, S_captive_prop = 0, R_captive_prop = 1)
ranch_rural.inits_alt8_steady <- initial_compartments(draws = nsamples, S_captive_prop = 0, R_captive_prop = 1, steady = T)

proj_ranch_rural_alt8 <- run(iter = nsamples, initial_compartments = ranch_rural.inits_alt8, initial_compartments_steady = ranch_rural.inits_alt8_steady, params = ranch_rural.params, times = times, name = "Vaccinate captive deer")

#9. Vaccinate and boost captive deer (start with r_captive = 1)
ranch_rural.inits_alt9 <- initial_compartments(draws = nsamples, S_captive_prop = 0, R_captive_prop = 1)
ranch_rural.inits_alt9_steady <- initial_compartments(draws = nsamples, S_captive_prop = 0, R_captive_prop = 1, steady = T)


boost_alt9 <- rep(0.9,nsamples)

ranch_rural.params_alt9 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_rural, omega_cw = omega_cw, omega_cc = omega_cc_ranch,
                            omega_hw = omega_hw_rural, omega_hc = omega_hc_ranch,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_rural, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_ranch, sigma_aero_deer_human_wild = sigma_aero_deer_human_rural, sigma_aero_deer_human_capt = sigma_aero_deer_human_ranch, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = boost_alt9)


proj_ranch_rural_alt9 <- run(iter = nsamples, initial_compartments = ranch_rural.inits_alt9, initial_compartments_steady = ranch_rural.inits_alt9_steady, params = ranch_rural.params_alt9, times = times, name = "Vaccinate and boost captive deer")

#10. Double fence captive facilities
omega_cw_alt10 <- rep(0, nsamples)

ranch_rural.params_alt10 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_rural, omega_cw = omega_cw_alt10, omega_cc = omega_cc_ranch,
                            omega_hw = omega_hw_rural, omega_hc = omega_hc_ranch,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_rural, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_ranch, sigma_aero_deer_human_wild = sigma_aero_deer_human_rural, sigma_aero_deer_human_capt = sigma_aero_deer_human_ranch, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0,nsamples))


proj_ranch_rural_alt10 <- run(iter = nsamples, initial_compartments = ranch_rural.inits.fall, initial_compartments_steady = ranch_rural.inits.steady, params = ranch_rural.params_alt10, times = times, name = "Double-fence captive facilities")

#11. Restrict human interaction (using proportional reduction from suburban to rural)
human_restrictions <- (get_EE_param_vals(data = elicitation_data, my_param = "Deer-Human Proximity Rate, Rural (per 120 days)") / 120)/(get_EE_param_vals(data = elicitation_data, my_param = "Deer-Human Proximity Rate, Suburban (per 120 days)") / 120)

ranch_rural.params_alt11 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_rural, omega_cw = omega_cw, omega_cc = omega_cc_ranch,
                            omega_hw = omega_hw_rural*human_restrictions, omega_hc = omega_hc_ranch,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_rural, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_ranch, sigma_aero_deer_human_wild = sigma_aero_deer_human_rural, sigma_aero_deer_human_capt = sigma_aero_deer_human_ranch, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0,nsamples))


proj_ranch_rural_alt11 <- run(iter = nsamples, initial_compartments = ranch_rural.inits.fall, initial_compartments_steady = ranch_rural.inits.steady, params = ranch_rural.params_alt11, times = times, name = "Restrict human interactions")

#12. Improve indoor facility air exchange (does not apply to outdoor ranch facilities)

proj_ranch_rural <- rbind(proj_ranch_rural_null, proj_ranch_rural_alt1, proj_ranch_rural_alt2, proj_ranch_rural_alt3, proj_ranch_rural_alt4, proj_ranch_rural_alt5, proj_ranch_rural_alt6, proj_ranch_rural_alt7, proj_ranch_rural_alt8, proj_ranch_rural_alt9, proj_ranch_rural_alt10, proj_ranch_rural_alt11)
```

#### Calculate prevalence, cumulative infections, and persistence for interventions in the outdoor ranch : wild, rural system
```{r, warning=FALSE, message=FALSE}
persist.threshold <- 0.001

proj_ranch_rural %>%
  mutate(steady_sir = map(steady_state, "y"),
         steady_sir = map(steady_sir, as_tibble_row)) %>%
  pull(steady_sir) %>%
  list_rbind(names_to = "run_id") %>%
  mutate(., persistWild = I_wild > persist.threshold, persistCaptive = I_captive > persist.threshold) %>%
  select(., run_id, persistWild, persistCaptive) %>%
  arrange(., run_id) -> Persist_ranch_rural_df

proj_ranch_rural %>%
  mutate(ode_df = map(ode_proj, as.data.frame)) %>%
  pull(ode_df) %>%
  list_rbind(names_to = "run_id") %>% 
  mutate(., Complex = rep("Outdoor ranch and rural deer",nrow(.)), Alternative = c(rep(unique(proj_ranch_rural$Context)[1],length(times)*nsamples),rep(unique(proj_ranch_rural$Context)[2],length(times)*nsamples), rep(unique(proj_ranch_rural$Context)[3],length(times)*nsamples),rep(unique(proj_ranch_rural$Context)[4],length(times)*nsamples), rep(unique(proj_ranch_rural$Context)[5],length(times)*nsamples), rep(unique(proj_ranch_rural$Context)[6],length(times)*nsamples), rep(unique(proj_ranch_rural$Context)[7],length(times)*nsamples),rep(unique(proj_ranch_rural$Context)[8],length(times)*nsamples),rep(unique(proj_ranch_rural$Context)[9],length(times)*nsamples),rep(unique(proj_ranch_rural$Context)[10],length(times)*nsamples),rep(unique(proj_ranch_rural$Context)[11],length(times)*nsamples),rep(unique(proj_ranch_rural$Context)[12],length(times)*nsamples))) %>% 
  group_by(Complex,Alternative, run_id) %>% 
  summarize(meanWild = mean(I_wild), meanCaptive = mean(I_captive), 
            cumulativeWild = last(I_wild_cumulative), cumulativeCaptive = last(I_captive_cumulative)) %>% 
   merge(.,Persist_ranch_rural_df, by = "run_id")-> alternatives_for_ranch_rural_complex
```

### Combined system of intensive captive facilities and wild deer in a suburban setting

```{r}
intensive_suburban.inits.fall <- initial_compartments(draws = nsamples)
intensive_suburban.inits.steady <- initial_compartments(draws = nsamples, steady = TRUE)


intensive_suburban.params <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_suburban, omega_cw = omega_cw, omega_cc = omega_cc_intensive,
                            omega_hw = omega_hw_suburban, omega_hc = omega_hc_intensive,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_suburban, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_intensive, sigma_aero_deer_human_wild = sigma_aero_deer_human_suburban, sigma_aero_deer_human_capt = sigma_aero_deer_human_intensive, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_intensive_suburban_null <- run(iter = nsamples, initial_compartments = intensive_suburban.inits.fall, initial_compartments_steady = intensive_suburban.inits.steady, params = intensive_suburban.params, times = times, name = "Baseline")

#Alternatives
#1. 10% density reduction
omega_ww_alt1_density.red.10 <- whitetailedSIRS::calc_contact_rate(nsamples = nsamples, type_contact = habitat, N_w = nWild*0.9)*(get_EE_param_vals(data = elicitation_data, my_param = "Proximity rate with baiting (17 events without baiting)")/17) 

intensive_suburban.params_alt1 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_alt1_density.red.10, omega_cw = omega_cw, omega_cc = omega_cc_intensive,
                            omega_hw = omega_hw_suburban, omega_hc = omega_hc_intensive,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_suburban, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_intensive, sigma_aero_deer_human_wild = sigma_aero_deer_human_suburban, sigma_aero_deer_human_capt = sigma_aero_deer_human_intensive, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_intensive_suburban_alt1 <- run(iter = nsamples, initial_compartments = intensive_suburban.inits.fall, initial_compartments_steady = intensive_suburban.inits.steady, params = intensive_suburban.params_alt1, times = times, name = "Reduce wild density by 10%")

#2. 25% density reduction
omega_ww_alt2_density.red.25 <- whitetailedSIRS::calc_contact_rate(nsamples = nsamples, type_contact = habitat, N_w = nWild*0.75)*(get_EE_param_vals(data = elicitation_data, my_param = "Proximity rate with baiting (17 events without baiting)")/17)

intensive_suburban.params_alt2 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_alt2_density.red.25, omega_cw = omega_cw, omega_cc = omega_cc_intensive,
                            omega_hw = omega_hw_suburban, omega_hc = omega_hc_intensive,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_suburban, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_intensive, sigma_aero_deer_human_wild = sigma_aero_deer_human_suburban, sigma_aero_deer_human_capt = sigma_aero_deer_human_intensive, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_intensive_suburban_alt2 <- run(iter = nsamples, initial_compartments = intensive_suburban.inits.fall, initial_compartments_steady = intensive_suburban.inits.steady, params = intensive_suburban.params_alt2, times = times, name = "Reduce wild density by 25%")

#3. Eliminate baiting
omega_ww_alt3_no.baiting <- whitetailedSIRS::calc_contact_rate(nsamples = nsamples, type_contact = habitat, N_w = nWild*0.75)

intensive_suburban.params_alt3 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_alt3_no.baiting, omega_cw = omega_cw, omega_cc = omega_cc_intensive,
                            omega_hw = omega_hw_suburban, omega_hc = omega_hc_intensive,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_suburban, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_intensive, sigma_aero_deer_human_wild = sigma_aero_deer_human_suburban, sigma_aero_deer_human_capt = sigma_aero_deer_human_intensive, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_intensive_suburban_alt3 <- run(iter = nsamples, initial_compartments = intensive_suburban.inits.fall, initial_compartments_steady = intensive_suburban.inits.steady, params = intensive_suburban.params_alt3, times = times, name = "Eliminate baiting")

#4. Pause research (assuming random 1-50% of human-wild deer interaction)
omega_hw_alt4_pause.research <- omega_hw_suburban*runif(nsamples, min = 0.5, max = 0.99) #reduce human deer proximity rate in the wild up to 50%

intensive_suburban.params_alt4 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_suburban, omega_cw = omega_cw, omega_cc = omega_cc_intensive,
                            omega_hw = omega_hw_alt4_pause.research, omega_hc = omega_hc_intensive,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_suburban, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_intensive, sigma_aero_deer_human_wild = sigma_aero_deer_human_suburban, sigma_aero_deer_human_capt = sigma_aero_deer_human_intensive, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_intensive_suburban_alt4 <- run(iter = nsamples, initial_compartments = intensive_suburban.inits.fall, initial_compartments_steady = intensive_suburban.inits.steady, params = intensive_suburban.params_alt4, times = times, name = "Pause Research")

#5. Require PPE for humans in wild settings
sigma_aero_deer_human_wild_alt5_PPE <- calc_sigma_aero(ER = 0.53, C_nu = C_nu_human, t_contact = t_contact_deer_human_suburban/60, r = r_deer, V_d = 0.009*runif(nsamples, min = (1-0.994), max = (1-0.509)), nsamples = nsamples)

intensive_suburban.params_alt5 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_suburban, omega_cw = omega_cw, omega_cc = omega_cc_intensive,
                            omega_hw = omega_hw_suburban, omega_hc = omega_hc_intensive,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_suburban, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_intensive, sigma_aero_deer_human_wild = sigma_aero_deer_human_wild_alt5_PPE, sigma_aero_deer_human_capt = sigma_aero_deer_human_intensive, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_intensive_suburban_alt5 <- run(iter = nsamples, initial_compartments = intensive_suburban.inits.fall, initial_compartments_steady = intensive_suburban.inits.steady, params = intensive_suburban.params_alt5, times = times, name = "PPE, Wild")

#6. Require PPE for humans in captive settings
sigma_aero_deer_human_capt_alt6_PPE <- calc_sigma_aero(ER = 0.53, C_nu = C_nu_human, t_contact = t_contact_deer_human_intensive/60, r = r_deer, V_d = 0.009*runif(nsamples, min = (1-0.994), max = (1-0.509)), nsamples = nsamples)

intensive_suburban.params_alt6 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_suburban, omega_cw = omega_cw, omega_cc = omega_cc_intensive,
                            omega_hw = omega_hw_suburban, omega_hc = omega_hc_intensive,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_suburban, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_intensive, sigma_aero_deer_human_wild = sigma_aero_deer_human_suburban, sigma_aero_deer_human_capt = sigma_aero_deer_human_capt_alt6_PPE, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_intensive_suburban_alt6 <- run(iter = nsamples, initial_compartments = intensive_suburban.inits.fall, initial_compartments_steady = intensive_suburban.inits.steady, params = intensive_suburban.params_alt6, times = times, name = "PPE, Captive")

#7. Require PPE for humans in wild and captive settings (use derived parameters from 5 and 6)

intensive_suburban.params_alt7 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_suburban, omega_cw = omega_cw, omega_cc = omega_cc_intensive,
                            omega_hw = omega_hw_suburban, omega_hc = omega_hc_intensive,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_suburban, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_intensive, sigma_aero_deer_human_wild = sigma_aero_deer_human_wild_alt5_PPE, sigma_aero_deer_human_capt = sigma_aero_deer_human_capt_alt6_PPE, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_intensive_suburban_alt7 <- run(iter = nsamples, initial_compartments = intensive_suburban.inits.fall, initial_compartments_steady = intensive_suburban.inits.steady, params =  intensive_suburban.params_alt7, times = times, name = "PPE, Both")

#8. Vaccinate captive deer (start with r_captive = 1)
intensive_suburban.inits_alt8.fall <- initial_compartments(draws = nsamples, S_captive_prop = 0, R_captive_prop = 1)
intensive_suburban.inits_alt8.steady <- initial_compartments(draws = nsamples, S_captive_prop = 0, R_captive_prop = 1, steady = TRUE)

proj_intensive_suburban_alt8 <- run(iter = nsamples, initial_compartments = intensive_suburban.inits_alt8.fall, initial_compartments_steady = intensive_suburban.inits_alt8.steady, params = intensive_suburban.params, times = times, name = "Vaccinate captive deer")

#9. Vaccinate and boost captive deer (start with r_captive = 1)
intensive_suburban.inits_alt9.fall <- initial_compartments(draws = nsamples, S_captive_prop = 0, R_captive_prop = 1)
intensive_suburban.inits_alt9.steady <- initial_compartments(draws = nsamples, S_captive_prop = 0, R_captive_prop = 1, steady = TRUE)

boost_alt9 <- rep(0.9,nsamples)

intensive_suburban.params_alt9 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_suburban, omega_cw = omega_cw, omega_cc = omega_cc_intensive,
                            omega_hw = omega_hw_suburban, omega_hc = omega_hc_intensive,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_suburban, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_intensive, sigma_aero_deer_human_wild = sigma_aero_deer_human_suburban, sigma_aero_deer_human_capt = sigma_aero_deer_human_intensive, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = boost_alt9)


proj_intensive_suburban_alt9 <- run(iter = nsamples, initial_compartments = intensive_suburban.inits_alt9.fall, initial_compartments_steady = intensive_suburban.inits_alt9.steady, params = intensive_suburban.params_alt9, times = times, name = "Vaccinate and boost captive deer")

#10. Double fence captive facilities
omega_cw_alt10 <- rep(0, nsamples)

intensive_suburban.params_alt10 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_suburban, omega_cw = omega_cw_alt10, omega_cc = omega_cc_intensive,
                            omega_hw = omega_hw_suburban, omega_hc = omega_hc_intensive,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_suburban, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_intensive, sigma_aero_deer_human_wild = sigma_aero_deer_human_suburban, sigma_aero_deer_human_capt = sigma_aero_deer_human_intensive, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0,nsamples))


proj_intensive_suburban_alt10 <- run(iter = nsamples, initial_compartments = intensive_suburban.inits.fall, initial_compartments_steady = intensive_suburban.inits.steady, params = intensive_suburban.params_alt10, times = times, name = "Double-fence captive facilities")

#11. Restrict human interaction (using proportional reduction from suburban to rural)
human_restrictions <- (get_EE_param_vals(data = elicitation_data, my_param = "Deer-Human Proximity Rate, Rural (per 120 days)") / 120)/(get_EE_param_vals(data = elicitation_data, my_param = "Deer-Human Proximity Rate, Suburban (per 120 days)") / 120)

intensive_suburban.params_alt11 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_suburban, omega_cw = omega_cw, omega_cc = omega_cc_intensive,
                            omega_hw = omega_hw_suburban*human_restrictions, omega_hc = omega_hc_intensive,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_suburban, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_intensive, sigma_aero_deer_human_wild = sigma_aero_deer_human_suburban, sigma_aero_deer_human_capt = sigma_aero_deer_human_intensive, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0,nsamples))


proj_intensive_suburban_alt11 <- run(iter = nsamples, initial_compartments = intensive_suburban.inits.fall, initial_compartments_steady = intensive_suburban.inits.steady, params = intensive_suburban.params_alt11, times = times, name = "Restrict human interactions")

#12. Improve indoor facility air exchange
sigma_aero_deer_human_intensive_alt12 <- calc_sigma_aero(ER = 0.53, C_nu = C_nu_human, t_contact = t_contact_deer_human_intensive/60, r = r_deer, nsamples = nsamples)

sigma_aero_deer_deer_intensive_alt12 <- calc_sigma_aero(C_nu = C_nu_deer, t_contact = t_contact_deer_deer_null/60, r = r_deer, nsamples = nsamples)

intensive_suburban.params_alt12 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_suburban, omega_cw = omega_cw, omega_cc = omega_cc_intensive,
                            omega_hw = omega_hw_suburban, omega_hc = omega_hc_intensive,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_suburban, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_intensive_alt12, sigma_aero_deer_human_wild = sigma_aero_deer_human_suburban, sigma_aero_deer_human_capt = sigma_aero_deer_human_intensive_alt12, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0,nsamples))


proj_intensive_suburban_alt12 <- run(iter = nsamples, initial_compartments = intensive_suburban.inits.fall, initial_compartments_steady = intensive_suburban.inits.steady, params = intensive_suburban.params_alt12, times = times, name = "Improve indoor facility air quality")

proj_intensive_suburban <- rbind(proj_intensive_suburban_null, proj_intensive_suburban_alt1, proj_intensive_suburban_alt2, proj_intensive_suburban_alt3, proj_intensive_suburban_alt4, proj_intensive_suburban_alt5, proj_intensive_suburban_alt6, proj_intensive_suburban_alt7, proj_intensive_suburban_alt8, proj_intensive_suburban_alt9, proj_intensive_suburban_alt10, proj_intensive_suburban_alt11, proj_intensive_suburban_alt12)
```

#### Calculate prevalence, cumulative infections, and persistence for interventions in the intensive facility : wild, suburban system

```{r, message=FALSE, warning=FALSE}
persist.threshold <- 0.001

proj_intensive_suburban %>%
  mutate(steady_sir = map(steady_state, "y"),
         steady_sir = map(steady_sir, as_tibble_row)) %>%
  pull(steady_sir) %>%
  list_rbind(names_to = "run_id") %>%
  mutate(., persistWild = I_wild > persist.threshold, persistCaptive = I_captive > persist.threshold) %>%
  select(., run_id, persistWild, persistCaptive) %>%
  arrange(., run_id) -> Persist_intensive_suburban_df


proj_intensive_suburban %>%
  mutate(ode_df = map(ode_proj, as.data.frame)) %>%
  pull(ode_df) %>%
  list_rbind(names_to = "run_id") %>% 
  mutate(., Complex = rep("Intensive facility and suburban deer",nrow(.)), Alternative = c(rep(unique(proj_intensive_suburban$Context)[1],length(times)*nsamples),rep(unique(proj_intensive_suburban$Context)[2],length(times)*nsamples), rep(unique(proj_intensive_suburban$Context)[3],length(times)*nsamples),rep(unique(proj_intensive_suburban$Context)[4],length(times)*nsamples), rep(unique(proj_intensive_suburban$Context)[5],length(times)*nsamples), rep(unique(proj_intensive_suburban$Context)[6],length(times)*nsamples), rep(unique(proj_intensive_suburban$Context)[7],length(times)*nsamples),rep(unique(proj_intensive_suburban$Context)[8],length(times)*nsamples),rep(unique(proj_intensive_suburban$Context)[9],length(times)*nsamples),rep(unique(proj_intensive_suburban$Context)[10],length(times)*nsamples),rep(unique(proj_intensive_suburban$Context)[11],length(times)*nsamples),rep(unique(proj_intensive_suburban$Context)[12],length(times)*nsamples), rep(unique(proj_intensive_suburban$Context)[13],length(times)*nsamples))) %>% 
  group_by(Complex,Alternative, run_id) %>% 
  summarize(meanWild = mean(I_wild), meanCaptive = mean(I_captive), 
            cumulativeWild = last(I_wild_cumulative), cumulativeCaptive = last(I_captive_cumulative)) %>% 
  merge(.,Persist_intensive_suburban_df, by = "run_id") -> alternatives_for_intensive_suburban_complex
```

### Combined system of intensive captive facilities and wild deer in a rural setting
```{r}
intensive_rural.inits.fall <- initial_compartments(draws = nsamples)
intensive_rural.inits.steady <- initial_compartments(draws = nsamples, steady = TRUE)


intensive_rural.params <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_rural, omega_cw = omega_cw, omega_cc = omega_cc_intensive,
                            omega_hw = omega_hw_rural, omega_hc = omega_hc_intensive,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_rural, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_intensive, sigma_aero_deer_human_wild = sigma_aero_deer_human_rural, sigma_aero_deer_human_capt = sigma_aero_deer_human_intensive, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_intensive_rural_null <- run(iter = nsamples, initial_compartments = intensive_rural.inits.fall, initial_compartments_steady = intensive_rural.inits.steady, params = intensive_rural.params, times = times, name = "Baseline")

#Alternatives
#1. 10% density reduction
omega_ww_alt1_density.red.10 <- whitetailedSIRS::calc_contact_rate(nsamples = nsamples, type_contact = habitat, N_w = nWild*0.9)*(get_EE_param_vals(data = elicitation_data, my_param = "Proximity rate with baiting (17 events without baiting)")/17) 

intensive_rural.params_alt1 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_alt1_density.red.10, omega_cw = omega_cw, omega_cc = omega_cc_intensive,
                            omega_hw = omega_hw_rural, omega_hc = omega_hc_intensive,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_rural, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_intensive, sigma_aero_deer_human_wild = sigma_aero_deer_human_rural, sigma_aero_deer_human_capt = sigma_aero_deer_human_intensive, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_intensive_rural_alt1 <- run(iter = nsamples, initial_compartments = intensive_rural.inits.fall, initial_compartments_steady = intensive_rural.inits.steady, params = intensive_rural.params_alt1, times = times, name = "Reduce wild density by 10%")

#2. 25% density reduction
omega_ww_alt2_density.red.25 <- whitetailedSIRS::calc_contact_rate(nsamples = nsamples, type_contact = habitat, N_w = nWild*0.75)*(get_EE_param_vals(data = elicitation_data, my_param = "Proximity rate with baiting (17 events without baiting)")/17)

intensive_rural.params_alt2 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_alt2_density.red.25, omega_cw = omega_cw, omega_cc = omega_cc_intensive,
                            omega_hw = omega_hw_rural, omega_hc = omega_hc_intensive,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_rural, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_intensive, sigma_aero_deer_human_wild = sigma_aero_deer_human_rural, sigma_aero_deer_human_capt = sigma_aero_deer_human_intensive, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_intensive_rural_alt2 <- run(iter = nsamples, initial_compartments = intensive_rural.inits.fall, initial_compartments_steady = intensive_rural.inits.steady, params = intensive_rural.params_alt2, times = times, name = "Reduce wild density by 25%")

#3. Eliminate baiting
omega_ww_alt3_no.baiting <- whitetailedSIRS::calc_contact_rate(nsamples = nsamples, type_contact = habitat, N_w = nWild*0.75)

intensive_rural.params_alt3 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_alt3_no.baiting, omega_cw = omega_cw, omega_cc = omega_cc_intensive,
                            omega_hw = omega_hw_rural, omega_hc = omega_hc_intensive,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_rural, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_intensive, sigma_aero_deer_human_wild = sigma_aero_deer_human_rural, sigma_aero_deer_human_capt = sigma_aero_deer_human_intensive, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_intensive_rural_alt3 <- run(iter = nsamples, initial_compartments = intensive_rural.inits.fall, initial_compartments_steady = intensive_rural.inits.steady, params = intensive_rural.params_alt3, times = times, name = "Eliminate baiting")

#4. Pause research (assuming random 1-50% of human-wild deer interaction)
omega_hw_alt4_pause.research <- omega_hw_rural*runif(nsamples, min = 0.5, max = 0.99) #reduce human deer proximity rate in the wild up to 50%

intensive_rural.params_alt4 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_rural, omega_cw = omega_cw, omega_cc = omega_cc_intensive,
                            omega_hw = omega_hw_alt4_pause.research, omega_hc = omega_hc_intensive,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_rural, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_intensive, sigma_aero_deer_human_wild = sigma_aero_deer_human_rural, sigma_aero_deer_human_capt = sigma_aero_deer_human_intensive, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_intensive_rural_alt4 <- run(iter = nsamples, initial_compartments = intensive_rural.inits.fall, initial_compartments_steady = intensive_rural.inits.steady, params = intensive_rural.params_alt4, times = times, name = "Pause Research")

#5. Require PPE for humans in wild settings
sigma_aero_deer_human_wild_alt5_PPE <- calc_sigma_aero(ER = 0.53, C_nu = C_nu_human, t_contact = t_contact_deer_human_rural/60, r = r_deer, V_d = 0.009*runif(nsamples, min = (1-0.994), max = (1-0.509)), nsamples = nsamples)

intensive_rural.params_alt5 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_rural, omega_cw = omega_cw, omega_cc = omega_cc_intensive,
                            omega_hw = omega_hw_rural, omega_hc = omega_hc_intensive,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_rural, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_intensive, sigma_aero_deer_human_wild = sigma_aero_deer_human_wild_alt5_PPE, sigma_aero_deer_human_capt = sigma_aero_deer_human_intensive, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_intensive_rural_alt5 <- run(iter = nsamples, initial_compartments = intensive_rural.inits.fall, initial_compartments_steady = intensive_rural.inits.steady, params = intensive_rural.params_alt5, times = times, name = "PPE, Wild")

#6. Require PPE for humans in captive settings
sigma_aero_deer_human_capt_alt6_PPE <- calc_sigma_aero(ER = 0.53, C_nu = C_nu_human, t_contact = t_contact_deer_human_intensive/60, r = r_deer, V_d = 0.009*runif(nsamples, min = (1-0.994), max = (1-0.509)), nsamples = nsamples)

intensive_rural.params_alt6 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_rural, omega_cw = omega_cw, omega_cc = omega_cc_intensive,
                            omega_hw = omega_hw_rural, omega_hc = omega_hc_intensive,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_rural, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_intensive, sigma_aero_deer_human_wild = sigma_aero_deer_human_rural, sigma_aero_deer_human_capt = sigma_aero_deer_human_capt_alt6_PPE, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_intensive_rural_alt6 <- run(iter = nsamples, initial_compartments = intensive_rural.inits.fall, initial_compartments_steady = intensive_rural.inits.steady, params = intensive_rural.params_alt6, times = times, name = "PPE, Captive")

#7. Require PPE for humans in wild and captive settings (use derived parameters from 5 and 6)

intensive_rural.params_alt7 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_rural, omega_cw = omega_cw, omega_cc = omega_cc_intensive,
                            omega_hw = omega_hw_rural, omega_hc = omega_hc_intensive,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_rural, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_intensive, sigma_aero_deer_human_wild = sigma_aero_deer_human_wild_alt5_PPE, sigma_aero_deer_human_capt = sigma_aero_deer_human_capt_alt6_PPE, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0, nsamples))

proj_intensive_rural_alt7 <- run(iter = nsamples, initial_compartments = intensive_rural.inits.fall, initial_compartments_steady = intensive_rural.inits.steady, params = intensive_rural.params_alt7, times = times, name = "PPE, Both")

#8. Vaccinate captive deer (start with r_captive = 1)
intensive_rural.inits.fall_alt8 <- initial_compartments(draws = nsamples, S_captive_prop = 0, R_captive_prop = 1)
intensive_rural.inits.steady_alt8 <- initial_compartments(draws = nsamples, S_captive_prop = 0, R_captive_prop = 1, steady = TRUE)

proj_intensive_rural_alt8 <- run(iter = nsamples, initial_compartments = intensive_rural.inits.fall_alt8, initial_compartments_steady = intensive_rural.inits.steady_alt8, params = intensive_rural.params, times = times, name = "Vaccinate captive deer")

#9. Vaccinate and boost captive deer (start with r_captive = 1)
intensive_rural.inits.fall_alt9 <- initial_compartments(draws = nsamples, S_captive_prop = 0, R_captive_prop = 1)
intensive_rural.inits.steady_alt9 <- initial_compartments(draws = nsamples, S_captive_prop = 0, R_captive_prop = 1, steady = TRUE)

boost_alt9 <- rep(0.9,nsamples)

intensive_rural.params_alt9 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_rural, omega_cw = omega_cw, omega_cc = omega_cc_intensive,
                            omega_hw = omega_hw_rural, omega_hc = omega_hc_intensive,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_rural, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_intensive, sigma_aero_deer_human_wild = sigma_aero_deer_human_rural, sigma_aero_deer_human_capt = sigma_aero_deer_human_intensive, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = boost_alt9)


proj_intensive_rural_alt9 <- run(iter = nsamples, initial_compartments = intensive_rural.inits.fall_alt9, initial_compartments_steady = intensive_rural.inits.steady_alt9, params = intensive_rural.params_alt9, times = times, name = "Vaccinate and boost captive deer")

#10. Double fence captive facilities
omega_cw_alt10 <- rep(0, nsamples)

intensive_rural.params_alt10 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_rural, omega_cw = omega_cw_alt10, omega_cc = omega_cc_intensive,
                            omega_hw = omega_hw_rural, omega_hc = omega_hc_intensive,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_rural, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_intensive, sigma_aero_deer_human_wild = sigma_aero_deer_human_rural, sigma_aero_deer_human_capt = sigma_aero_deer_human_intensive, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0,nsamples))


proj_intensive_rural_alt10 <- run(iter = nsamples, initial_compartments = intensive_rural.inits.fall, initial_compartments_steady = intensive_rural.inits.steady, params = intensive_rural.params_alt10, times = times, name = "Double-fence captive facilities")

#11. Restrict human interaction (using proportional reduction from suburban to rural)
human_restrictions <- (get_EE_param_vals(data = elicitation_data, my_param = "Deer-Human Proximity Rate, Rural (per 120 days)") / 120)/(get_EE_param_vals(data = elicitation_data, my_param = "Deer-Human Proximity Rate, Suburban (per 120 days)") / 120)

intensive_rural.params_alt11 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_rural, omega_cw = omega_cw, omega_cc = omega_cc_intensive,
                            omega_hw = omega_hw_rural*human_restrictions, omega_hc = omega_hc_intensive,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_rural, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_intensive, sigma_aero_deer_human_wild = sigma_aero_deer_human_rural, sigma_aero_deer_human_capt = sigma_aero_deer_human_intensive, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0,nsamples))


proj_intensive_rural_alt11 <- run(iter = nsamples, initial_compartments = intensive_rural.inits.fall, initial_compartments_steady = intensive_rural.inits.steady, params = intensive_rural.params_alt11, times = times, name = "Restrict human interactions")

#12. Improve indoor facility air exchange
sigma_aero_deer_human_intensive_alt12 <- calc_sigma_aero(ER = 0.53, C_nu = C_nu_human, t_contact = t_contact_deer_human_intensive/60, r = r_deer, nsamples = nsamples)

sigma_aero_deer_deer_intensive_alt12 <- calc_sigma_aero(C_nu = C_nu_deer, t_contact = t_contact_deer_deer_null/60, r = r_deer, nsamples = nsamples)

intensive_rural.params_alt12 <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_rural, omega_cw = omega_cw, omega_cc = omega_cc_intensive,
                            omega_hw = omega_hw_rural, omega_hc = omega_hc_intensive,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_rural, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_intensive_alt12, sigma_aero_deer_human_wild = sigma_aero_deer_human_rural, sigma_aero_deer_human_capt = sigma_aero_deer_human_intensive_alt12, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = rep(0,nsamples))


proj_intensive_rural_alt12 <- run(iter = nsamples, initial_compartments = intensive_rural.inits.fall, initial_compartments_steady = intensive_rural.inits.steady, params = intensive_rural.params_alt12, times = times, name = "Improve indoor facility air quality")

proj_intensive_rural <- rbind(proj_intensive_rural_null, proj_intensive_rural_alt1, proj_intensive_rural_alt2, proj_intensive_rural_alt3, proj_intensive_rural_alt4, proj_intensive_rural_alt5, proj_intensive_rural_alt6, proj_intensive_rural_alt7, proj_intensive_rural_alt8, proj_intensive_rural_alt9, proj_intensive_rural_alt10, proj_intensive_rural_alt11, proj_intensive_rural_alt12)
```

#### Calculate prevalence, cumulative infections, and persistence for interventions in the intensive facility : wild, rural system

```{r, message = FALSE, warning=FALSE}
persist.threshold <- 0.001

proj_intensive_rural %>%
  mutate(steady_sir = map(steady_state, "y"),
         steady_sir = map(steady_sir, as_tibble_row)) %>%
  pull(steady_sir) %>%
  list_rbind(names_to = "run_id") %>%
  mutate(., persistWild = I_wild > persist.threshold, persistCaptive = I_captive > persist.threshold) %>%
  select(., run_id, persistWild, persistCaptive) %>%
  arrange(., run_id) -> Persist_intensive_rural_df

proj_intensive_rural %>%
  mutate(ode_df = map(ode_proj, as.data.frame)) %>%
  pull(ode_df) %>%
  list_rbind(names_to = "run_id") %>% 
  mutate(., Complex = rep("Intensive facility and rural deer",nrow(.)), Alternative = c(rep(unique(proj_intensive_rural$Context)[1],length(times)*nsamples),rep(unique(proj_intensive_rural$Context)[2],length(times)*nsamples), rep(unique(proj_intensive_rural$Context)[3],length(times)*nsamples),rep(unique(proj_intensive_rural$Context)[4],length(times)*nsamples), rep(unique(proj_intensive_rural$Context)[5],length(times)*nsamples), rep(unique(proj_intensive_rural$Context)[6],length(times)*nsamples), rep(unique(proj_intensive_rural$Context)[7],length(times)*nsamples),rep(unique(proj_intensive_rural$Context)[8],length(times)*nsamples),rep(unique(proj_intensive_rural$Context)[9],length(times)*nsamples),rep(unique(proj_intensive_rural$Context)[10],length(times)*nsamples),rep(unique(proj_intensive_rural$Context)[11],length(times)*nsamples),rep(unique(proj_intensive_rural$Context)[12],length(times)*nsamples), rep(unique(proj_intensive_rural$Context)[13],length(times)*nsamples))) %>% 
  group_by(Complex,Alternative, run_id) %>% 
  summarize(meanWild = mean(I_wild), meanCaptive = mean(I_captive), 
            cumulativeWild = last(I_wild_cumulative), cumulativeCaptive = last(I_captive_cumulative)) %>% 
  merge(.,Persist_intensive_rural_df, by = "run_id") -> alternatives_for_intensive_rural_complex
```

### Combine and summarize results

Below, we combine the results for all alternatives, for all combinations of captive and wild scenarios (systems). These results are saved in the package's data folder, and can be accessed through `whitetailedSIRS::alternatives_across_systems`.

```{r}
alternatives_across_systems <- rbind(alternatives_for_ranch_suburban_complex, alternatives_for_ranch_rural_complex, alternatives_for_intensive_suburban_complex, alternatives_for_intensive_rural_complex)

alternatives_across_systems %>% 
   group_by(., Complex, Alternative) %>% 
   summarize(., Wild_Cumulative = median(cumulativeWild), Captive_Cumulative = median(cumulativeCaptive))

```

##Test Impact of Cross-Sector Collaboration
Finally, we simulated SARS-CoV-2 outbreaks in each system with multiple alternatives applied. Here, we implement the most effective alternative for each sector (agriculture, public health, and wildlife) in concert to understand the cumulative effects of coordinated actions across sectors. The results of this final simulation are stored in `whitetailedSIRS::cross_sector_results`.

```{r}
#Vaccinate..
cross_sector.inits.fall <- initial_compartments(draws = nsamples, S_captive_prop = 0, R_captive_prop = 1)
cross_sector.inits.steady <- initial_compartments(draws = nsamples, S_captive_prop = 0, R_captive_prop = 1, steady = TRUE)

#...and boost
boost_alt9 <- rep(0.9,nsamples)

#PPE for all interactions
sigma_aero_deer_human_capt_alt6_PPE <- calc_sigma_aero(ER = 0.53, C_nu = C_nu_human, t_contact = t_contact_deer_human_ranch/60, r = r_deer, V_d = 0.009*runif(nsamples, min = (1-0.994), max = (1-0.509)), nsamples = nsamples)

sigma_aero_deer_human_wild_alt5_PPE <- calc_sigma_aero(ER = 0.53, C_nu = C_nu_human, t_contact = t_contact_deer_human_rural/60, r = r_deer, V_d = 0.009*runif(nsamples, min = (1-0.994), max = (1-0.509)), nsamples = nsamples)

#Eliminate baiting
omega_ww_alt3_no.baiting <- whitetailedSIRS::calc_contact_rate(nsamples = nsamples, type_contact = habitat, N_w = nWild*0.75)

#Ranch and suburban complex
ranch_suburban_cross_sector.params <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_alt3_no.baiting, omega_cw = omega_cw, omega_cc = omega_cc_ranch,
                            omega_hw = omega_hw_suburban, omega_hc = omega_hc_ranch,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_suburban, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_ranch, sigma_aero_deer_human_wild = sigma_aero_deer_human_wild_alt5_PPE, sigma_aero_deer_human_capt = sigma_aero_deer_human_capt_alt6_PPE, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = boost_alt9)

proj_ranch_suburban_cross_sector <- run(iter = nsamples, initial_compartments = cross_sector.inits.fall, initial_compartments_steady = cross_sector.inits.steady, params =  ranch_suburban_cross_sector.params, times = times, name = "Cross-Sector Collaboration: Vaccinate and Boost, PPE for all interactions, and eliminating baiting")

proj_ranch_suburban_cross_sector %>%
  mutate(steady_sir = map(steady_state, "y"),
         steady_sir = map(steady_sir, as_tibble_row)) %>%
  pull(steady_sir) %>%
  list_rbind(names_to = "run_id") %>%
  mutate(., persistWild = I_wild > persist.threshold, persistCaptive = I_captive > persist.threshold) %>%
  select(., run_id, persistWild, persistCaptive) %>%
  arrange(., run_id) -> Persist_ranch_suburban_cross_sector_df

proj_ranch_suburban_cross_sector %>%
  mutate(ode_df = map(ode_proj, as.data.frame)) %>%
  pull(ode_df) %>%
  list_rbind(names_to = "run_id") %>% 
  mutate(., Complex = rep("Ranch and suburban deer",nrow(.)), Alternative = c(rep(unique(proj_ranch_suburban_cross_sector$Context)[1],length(times)*nsamples))) %>% 
  group_by(Complex,Alternative, run_id) %>% 
  summarize(meanWild = mean(I_wild), meanCaptive = mean(I_captive), 
            cumulativeWild = last(I_wild_cumulative), cumulativeCaptive = last(I_captive_cumulative)) %>% 
   merge(.,Persist_ranch_suburban_cross_sector_df, by = "run_id") -> cross_sector_for_ranch_suburban_complex

#Ranch and rural complex
ranch_rural_cross_sector.params <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_alt3_no.baiting, omega_cw = omega_cw, omega_cc = omega_cc_ranch,
                            omega_hw = omega_hw_rural, omega_hc = omega_hc_ranch,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_rural, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_ranch, sigma_aero_deer_human_wild = sigma_aero_deer_human_wild_alt5_PPE, sigma_aero_deer_human_capt = sigma_aero_deer_human_capt_alt6_PPE, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = boost_alt9)

proj_ranch_rural_cross_sector <- run(iter = nsamples, initial_compartments = cross_sector.inits.fall, initial_compartments_steady = cross_sector.inits.steady, params = ranch_rural_cross_sector.params, times = times, name = "Cross-Sector Collaboration: Vaccinate and Boost, PPE for all interactions, and eliminating baiting")

proj_ranch_rural_cross_sector %>%
  mutate(steady_sir = map(steady_state, "y"),
         steady_sir = map(steady_sir, as_tibble_row)) %>%
  pull(steady_sir) %>%
  list_rbind(names_to = "run_id") %>%
  mutate(., persistWild = I_wild > persist.threshold, persistCaptive = I_captive > persist.threshold) %>%
  select(., run_id, persistWild, persistCaptive) %>%
  arrange(., run_id) -> Persist_ranch_rural_cross_sector_df

proj_ranch_rural_cross_sector %>%
  mutate(ode_df = map(ode_proj, as.data.frame)) %>%
  pull(ode_df) %>%
  list_rbind(names_to = "run_id") %>% 
  mutate(., Complex = rep("Ranch and rural deer",nrow(.)), Alternative = c(rep(unique(proj_ranch_rural_cross_sector$Context)[1],length(times)*nsamples))) %>% 
  group_by(Complex,Alternative, run_id) %>% 
  summarize(meanWild = mean(I_wild), meanCaptive = mean(I_captive), 
            cumulativeWild = last(I_wild_cumulative), cumulativeCaptive = last(I_captive_cumulative)) %>% 
  merge(.,Persist_ranch_rural_cross_sector_df, by = "run_id")-> cross_sector_for_ranch_rural_complex

#Intensive facility and suburban complex
intensive_suburban_cross_sector.params <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_alt3_no.baiting, omega_cw = omega_cw, omega_cc = omega_cc_intensive,
                            omega_hw = omega_hw_suburban, omega_hc = omega_hc_intensive,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_suburban, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_intensive, sigma_aero_deer_human_wild = sigma_aero_deer_human_wild_alt5_PPE, sigma_aero_deer_human_capt = sigma_aero_deer_human_capt_alt6_PPE, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = boost_alt9)

proj_intensive_suburban_cross_sector <- run(iter = nsamples, initial_compartments = cross_sector.inits.fall, initial_compartments_steady = cross_sector.inits.steady, params = intensive_suburban_cross_sector.params, times = times, name = "Cross-Sector Collaboration: Vaccinate and Boost, PPE for all interactions, and eliminating baiting")

proj_intensive_suburban_cross_sector %>%
  mutate(steady_sir = map(steady_state, "y"),
         steady_sir = map(steady_sir, as_tibble_row)) %>%
  pull(steady_sir) %>%
  list_rbind(names_to = "run_id") %>%
  mutate(., persistWild = I_wild > persist.threshold, persistCaptive = I_captive > persist.threshold) %>%
  select(., run_id, persistWild, persistCaptive) %>%
  arrange(., run_id) -> Persist_intensive_suburban_cross_sector_df

proj_intensive_suburban_cross_sector %>%
  mutate(ode_df = map(ode_proj, as.data.frame)) %>%
  pull(ode_df) %>%
  list_rbind(names_to = "run_id") %>% 
  mutate(., Complex = rep("Intensive facility and suburban deer",nrow(.)), Alternative = c(rep(unique(proj_intensive_suburban_cross_sector$Context)[1],length(times)*nsamples))) %>% 
  group_by(Complex,Alternative, run_id) %>% 
  summarize(meanWild = mean(I_wild), meanCaptive = mean(I_captive), 
            cumulativeWild = last(I_wild_cumulative), cumulativeCaptive = last(I_captive_cumulative)) %>% 
   merge(.,Persist_intensive_suburban_cross_sector_df, by = "run_id")-> cross_sector_for_intensive_suburban_complex

#Intensive facility and rural complex
intensive_rural_cross_sector.params <- alternative(alpha_immunity = alpha_immunity_null,
                            omega_ww = omega_ww_alt3_no.baiting, omega_cw = omega_cw, omega_cc = omega_cc_intensive,
                            omega_hw = omega_hw_rural, omega_hc = omega_hc_intensive,
                            sigma_aero_deer_deer_wild = sigma_aero_deer_deer_rural, sigma_aero_deer_deer_captive = sigma_aero_deer_deer_intensive, sigma_aero_deer_human_wild = sigma_aero_deer_human_wild_alt5_PPE, sigma_aero_deer_human_capt = sigma_aero_deer_human_capt_alt6_PPE, epsilon_dc = epsilon_dc, sigma_dc_deer_deer = sigma_dc_deer_deer_null, gamma_recov = gamma_recov, I_human = rep(I_human_null, nsamples), boost = boost_alt9)

proj_intensive_rural_cross_sector <- run(iter = nsamples, initial_compartments = cross_sector.inits.fall, initial_compartments_steady = cross_sector.inits.steady, params = intensive_rural_cross_sector.params, times = times, name = "Cross-Sector Collaboration: Vaccinate and Boost, PPE for all interactions, and eliminating baiting")

proj_intensive_rural_cross_sector %>%
  mutate(steady_sir = map(steady_state, "y"),
         steady_sir = map(steady_sir, as_tibble_row)) %>%
  pull(steady_sir) %>%
  list_rbind(names_to = "run_id") %>%
  mutate(., persistWild = I_wild > persist.threshold, persistCaptive = I_captive > persist.threshold) %>%
  select(., run_id, persistWild, persistCaptive) %>%
  arrange(., run_id) -> Persist_intensive_rural_cross_sector_df

proj_intensive_rural_cross_sector %>%
  mutate(ode_df = map(ode_proj, as.data.frame)) %>%
  pull(ode_df) %>%
  list_rbind(names_to = "run_id") %>% 
  mutate(., Complex = rep("Intensive facility and rural deer",nrow(.)), Alternative = c(rep(unique(proj_intensive_rural_cross_sector$Context)[1],length(times)*nsamples))) %>% 
  group_by(Complex,Alternative, run_id) %>% 
  summarize(meanWild = mean(I_wild), meanCaptive = mean(I_captive), 
            cumulativeWild = last(I_wild_cumulative), cumulativeCaptive = last(I_captive_cumulative)) %>% 
   merge(.,Persist_intensive_rural_cross_sector_df, by = "run_id")-> cross_sector_for_intensive_rural_complex


cross_sector_results <- rbind(cross_sector_for_ranch_suburban_complex, cross_sector_for_ranch_rural_complex, cross_sector_for_intensive_suburban_complex, cross_sector_for_intensive_rural_complex)

cross_sector_results %>% 
   group_by(Complex) %>% 
   summarize(., prevalenceWild = median(meanWild), prevalenceCaptive = median(meanCaptive), cumulativeWild = median(cumulativeWild), cumulativeCaptive = median(cumulativeCaptive), meanPersistWild = (sum(persistWild)/nsamples), meanPersistCaptive= (sum(persistCaptive)/nsamples))

```
